DNSKEY Management

### 2012-12-04 paper/paper.tex
Add chain of trust to introduction, yet to fill
latest.

\subsection{Signing a zone}
Whenever an entity wishes to sign its zone, it should ideally turn to its already signed parent zone, in order to create a continuous trust chain, as said parent will then serve a DS record containing the child zone's key signature.

@@

\subsubsection{Single administrative domain}
Basically, once an organisation has its main domain signed, it is relatively easy for any sub-entity within said organisation to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key roll-over: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant for such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are.
\subsection{Disabling DNSSEC}

\section{Case-Study: \texttt{ch.} Zone\wbts}
\label{sec:case-study}

The \verb|ch.| zone is managed by SWITCH, the institution which also
employs the Swiss educational network. In this section we briefly
point out the current deployment status of DNSSEC and how SWITCH
handles the discussed key management issues.

\paragraph{Certificate Chain} According to a query on SecSpider
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
verifiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.

>>>>

\subsection{Signing a zone}
Whenever an entity wishes to sign its zone, it should ideally turn to its already signed parent zone, in order to create a continuous thrust chain.
Said parent should then serve a DS record containing the child zone's key signature.

@@

\subsubsection{Single administrative domain}
Basically, once an organisation has its main domain signed, it is relatively easy for any sub-entity within said organisation to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key roll-over: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
\subsection{Disabling DNSSEC}

\section{Case-Study: Switzerland (\texttt{ch.} Zone)\wbts}
\label{sec:case-study}

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
verifiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.
